Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-19 tex/v3/appendix.tex
new figure

\begin{figure*}[t]
	\centering

	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl10.pdf}
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl10.pdf}
	\caption{OT Domain Adaptation on a toy problem : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
	%~\hfill~	\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~\\
	~\hfill~\includegraphics[width=6.cm]{../../figure/wda_accur_toy.pdf}~\hfill~
	\includegraphics[width=6.cm]{../../figure/wda_accur_mnist.pdf}~\hfill~\\
	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem.
		(right) MNIST). We note a slight loss of performance for the toy problem, whereas for MNIST, all approaches yield the same performance. 
		\label{fig:wda_gain}}
\end{figure*}

\begin{figure*}[t]
	\centering
	%~\hfill~	\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~\\
	~\hfill~\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl100.pdf}~\hfill~\\
	~\hfill~\includegraphics[width=6.cm]{../../figure/da_time_toy_regcl100.pdf}
	~\hfill~\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl100.pdf}~\hfill~\\
	\caption{OT Domain Adaptation on a 3-class Gaussian toy problem. (top-left) Examples of source and target samples. (top-right) Evolution of the accuracy of a 1-nearest-neighbour classifier with respect to the number of samples. (bottom-left) Running time of the \emph{Sinkhorn} and \emph{Screenkhorn} for different decimation
	factors. (bottom-right). Gain in computation time. This toy problem is a problem in which classes are overlapping and distance between samples are rather limited. According to our analysis, this may be a situation in which \emph{Screenkhorn} may
	result in smaller computational gain. We can remark that with respect to the accuracy
	\emph{Screenkhorn} with decimation factors up to $10$ are competitive with \emph{Sinkhorn}, although a slight loss of performance. Regarding computational time, for this example, small decimation factors does not  result in gain. However for above  $5$-factor decimation, the gain goes from  $2$ to $10$ depending on
	the number of samples. 
	\label{fig:otda}}
\end{figure*}

### 2019-05-19 tex/v3/section_5_numeric_expes.tex
new figure

Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
Analysis of the quality of the subspace have been deported to the supplementary material, but we can remark a small loss of performance of Screenkhorn for the toy problem, while
for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
that for the minimal gains are respectively $2$ and $4.5$ for the toy and MNIST problem
whereas the maximal gain for $4000$ samples is slightly larger than an order of magnitude.

@@

For the optimal transport based domain adaptation problem, we have considered the
OTDA with $\ell_{0.5,1}$ group-lasso regularizer that helps in exploiting available labels in the source domain. The problem is solved using an majorization-minimization approach 
for handling the non-convexity of the problem. Hence, at each iteration, a Sinkhorn/Screenkhorn has to be computed. As a domain-adaptation problem, we have
used a MNIST to USPS problem in which features have been extracted from the
feature extractor of an domain adversarial neural networks \cite{ganin2016domain} before full
convergence of the networks (so as to leave room for OT adaptation).

>>>>

Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
Analysis of the quality of the subspace have been deported to the supplementary material (see Figure \ref{}), but we can remark a small loss of performance of Screenkhorn for the toy problem, while
for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
that for the minimal gains are respectively $2$ and $4.5$ for the toy and MNIST problem
whereas the maximal gain for $4000$ samples is slightly larger than an order of magnitude.

@@

For the optimal transport based domain adaptation problem, we have considered the
OTDA with $\ell_{0.5,1}$ group-lasso regularizer that helps in exploiting available labels in the source domain. The problem is solved using an majorization-minimization approach 
for handling the non-convexity of the problem. Hence, at each iteration, a Sinkhorn/Screenkhorn has to be computed. As a domain-adaptation problem, we have
used a MNIST to USPS problem in which features have been extracted from the
feature extractor of an domain adversarial neural networks \cite{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
Figure \ref{fig:otda} reports the gain in running time for $2$ fifferent values
of the group-lasso regularizer hyperparameter, while the curves of performances are
reported in the supplementary material. We can note that for all the  \emph{Screenkhorn} with different decimation factors, the gain in computation goes from a factor of $4$ to $12$, while accuracies are somewhat equivalent.
